New insights into the Weddell Sea ecosystem applying a network approach

### 2022-08-05 Manuscript/Manuscript.Rmd
Added Figs 1-3

**Important**: Always double-check with the official manuscript
preparation guidelines at
<https://publications.copernicus.org/for_authors/manuscript_preparation.html>,
especially the sections "Technical instructions for LaTeX" and
"Manuscript composition". Please contact Daniel Nüst,
`daniel.nuest@uni-muenster.de`, with any problems.

@@

The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS with a length of approximately 450 km. Water depth varies from 200 to 500 m. Shallower areas are covered by continental ice, which forms the coastline along the eastern and southern part of the Weddell Sea. The shelf area contains a complex three-dimensional habitat with large biomass, intermediate to high diversity in comparison to benthic boreal communities and a spatially patchy distribution of organisms [@Dayton1990, @Teixido2002].

Add Figure of map.

## Weddell Sea food web data set

We obtained the data set of the Weddell Sea food web from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018].
This marine food web, which includes all the food web data available for the high Antarctic Weddell Sea collected 
since 1983, is one of the most highly resolved marine food webs documented to date. It's noteworthy that it is a 
summary network that ignores seasonal changes [@Jacob2011].

@@

In order to characterize the species, we considered weighted and unweighted properties. The former is based on the estimation of the interaction strength described in the previous section. The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991, @Dunne2002, @Borrelli2014]. As weighted property we used the mean interaction strength, meaning the average strength of all species interactions. As unweighted properties we used: a) degree or the total number of trophic interactions taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the measurement of trophic overlap between species based on shared and unique resources and consumers.

Add Figure of toy food web.

@@

See the [R Markdown docs for bibliographies and
citations](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html).

Copernicus supports biblatex and a sample bibliography is in file
`WeddellSea.bib`. Read [@Pawar2012], and [see @Dirac1953888].

@@

If you want to insert a list, you must

-   leave

-   empty lines

-   between each list item

because the `\tightlist` format used by R Markdown is not supported in
the Copernicus template. Example:

    - leave

    - empty lines

    - between each list item

@@

Include a 12cm width figure of Nikolaus Copernicus from
[Wikipedia](https://en.wikipedia.org/wiki/File:Nikolaus_Kopernikus.jpg)
with caption using R Markdown.

@@

You can also include a larger figure.

>>>>

@@

The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS with a length of approximately 450 km (Figure 1). Water depth varies from 200 to 500 m. Shallower areas are covered by continental ice, which forms the coastline along the eastern and southern part of the Weddell Sea. The shelf area contains a complex three-dimensional habitat with large biomass, intermediate to high diversity in comparison to benthic boreal communities and a spatially patchy distribution of organisms [@Dayton1990; @Teixido2002].

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour. Modified from www.soos.aq."}
knitr::include_graphics("WeddellSea_map.jpg")
```

## Weddell Sea food web dataset

We obtained the dataset of the Weddell Sea food web from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018]. This open access database is a list of predator-prey interactions that describe several highly-resolved food webs, including biological data about the consumer and resource involved in each trophic interaction (i.e. mean mass). Furthermore, it incorporates information on the interaction itself, such as the dimensionality.
This marine food web compiles all the food web data available for the high Antarctic Weddell Sea collected 
since 1983, and is one of the most highly-resolved marine food webs documented to date. It's noteworthy that it is a 
summary network that ignores seasonal changes [@Jacob2011].

@@

In order to characterize the species, we considered weighted and unweighted properties (Figure 2). The former is based on the estimation of the interaction strength described in the previous section. The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014]. As weighted property we used the mean interaction strength, meaning the average strength of all species interactions. As unweighted properties we used: a) degree or the total number of trophic interactions taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the measurement of trophic overlap between species based on shared and unique resources and consumers.

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web."}
knitr::include_graphics("ToyFoodWeb.jpg")
```

@@

The Weddell Sea food web comprises 490 species and 16041 predator-prey interactions (Figure 3).

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Graphic representation of the Weddell Sea food web. Species (nodes) are arranged verticaly and colored by trophic level. The diameter of the node indicates the total number of interactions. Predator-prey interactions are represented by the arrows, from the prey to the predator."}
knitr::include_graphics("WeddellSea_net.jpg")
```

@@

@@

@@

### 2022-08-05 Manuscript/Manuscript.tex
Added Figs 1-3

\textbf{Important}: Always double-check with the official manuscript
preparation guidelines at
\url{https://publications.copernicus.org/for_authors/manuscript_preparation.html},
especially the sections ``Technical instructions for LaTeX'' and
``Manuscript composition''. Please contact Daniel Nüst,
\texttt{daniel.nuest@uni-muenster.de}, with any problems.

@@

The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS
with a length of approximately 450 km. Water depth varies from 200 to
500 m. Shallower areas are covered by continental ice, which forms the
coastline along the eastern and southern part of the Weddell Sea. The
shelf area contains a complex three-dimensional habitat with large
biomass, intermediate to high diversity in comparison to benthic boreal
communities and a spatially patchy distribution of organisms
\citep[\citet{Teixido2002}]{Dayton1990}.

Add Figure of map.

\subsection{Weddell Sea food web data set}

We obtained the data set of the Weddell Sea food web from the GlobAL
daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of
the German Centre for Integrative Biodiversity Research (iDiv)
Halle-Jena-Leipzig \citep{Brose2018}. This marine food web, which
includes all the food web data available for the high Antarctic Weddell
Sea collected since 1983, is one of the most highly resolved marine food
webs documented to date. It's noteworthy that it is a summary network
that ignores seasonal changes \citep{Jacob2011}.

@@

In order to characterize the species, we considered weighted and
unweighted properties. The former is based on the estimation of the
interaction strength described in the previous section. The latter is
related to properties commonly used in qualitative (presence/absence of
interaction) food web studies \citep[\citet{Dunne2002},
\citet{Borrelli2014}]{Martinez1991}. As weighted property we used the
mean interaction strength, meaning the average strength of all species
interactions. As unweighted properties we used: a) degree or the total
number of trophic interactions taking into account in- and
out-interactions (role as predator and prey, respectively); b) trophic
level or the position in the food web relative to primary
producers/detritus; and c) trophic similarity or the measurement of
trophic overlap between species based on shared and unique resources and
consumers.

Add Figure of toy food web.

@@

See the
\href{http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html}{R
Markdown docs for bibliographies and citations}.

Copernicus supports biblatex and a sample bibliography is in file
\texttt{WeddellSea.bib}. Read \citep{Pawar2012}, and
\citep[see][]{Dirac1953888}.

@@

If you want to insert a list, you must

\begin{itemize}
\item
  leave
\item
  empty lines
\item
  between each list item
\end{itemize}

because the \texttt{\textbackslash{}tightlist} format used by R Markdown
is not supported in the Copernicus template. Example:

\begin{verbatim}
- leave

- empty lines

- between each list item
\end{verbatim}

@@

Include a 12cm width figure of Nikolaus Copernicus from
\href{https://en.wikipedia.org/wiki/File:Nikolaus_Kopernikus.jpg}{Wikipedia}
with caption using R Markdown.

\begin{figure}
\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-2}
\end{figure}

@@

You can also include a larger figure.

\begin{figure}
\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-3}
\end{figure}

>>>>

@@

The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS
with a length of approximately 450 km (Figure 1). Water depth varies
from 200 to 500 m. Shallower areas are covered by continental ice, which
forms the coastline along the eastern and southern part of the Weddell
Sea. The shelf area contains a complex three-dimensional habitat with
large biomass, intermediate to high diversity in comparison to benthic
boreal communities and a spatially patchy distribution of organisms
\citep{Dayton1990, Teixido2002}.

\begin{figure}
\includegraphics[width=12cm]{WeddellSea_map} \caption{Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour. Modified from www.soos.aq.}\label{fig:unnamed-chunk-1}
\end{figure}

\subsection{Weddell Sea food web dataset}

We obtained the dataset of the Weddell Sea food web from the GlobAL
daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of
the German Centre for Integrative Biodiversity Research (iDiv)
Halle-Jena-Leipzig \citep{Brose2018}. This open access database is a
list of predator-prey interactions that describe several highly-resolved
food webs, including biological data about the consumer and resource
involved in each trophic interaction (i.e.~mean mass). Furthermore, it
incorporates information on the interaction itself, such as the
dimensionality. This marine food web compiles all the food web data
available for the high Antarctic Weddell Sea collected since 1983, and
is one of the most highly-resolved marine food webs documented to date.
It's noteworthy that it is a summary network that ignores seasonal
changes \citep{Jacob2011}.

@@

In order to characterize the species, we considered weighted and
unweighted properties (Figure 2). The former is based on the estimation
of the interaction strength described in the previous section. The
latter is related to properties commonly used in qualitative
(presence/absence of interaction) food web studies
\citep{Martinez1991, Dunne2002, Borrelli2014}. As weighted property we
used the mean interaction strength, meaning the average strength of all
species interactions. As unweighted properties we used: a) degree or the
total number of trophic interactions taking into account in- and
out-interactions (role as predator and prey, respectively); b) trophic
level or the position in the food web relative to primary
producers/detritus; and c) trophic similarity or the measurement of
trophic overlap between species based on shared and unique resources and
consumers.

\begin{figure}
\includegraphics[width=12cm]{ToyFoodWeb} \caption{Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web.}\label{fig:unnamed-chunk-2}
\end{figure}

@@

The Weddell Sea food web comprises 490 species and 16041 predator-prey
interactions (Figure 3).

\begin{figure}
\includegraphics[width=12cm]{WeddellSea_net} \caption{Graphic representation of the Weddell Sea food web. Species (nodes) are arranged verticaly and colored by trophic level. The diameter of the node indicates the total number of interactions. Predator-prey interactions are represented by the arrows, from the prey to the predator.}\label{fig:unnamed-chunk-3}
\end{figure}

@@

@@

\begin{figure}
\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-6}
\end{figure}
